# Cleaning and summarizing the data



```{r include = TRUE}
library(dplyr)
library(tidyr)
```

function to calculate returns 
```{r}
percentage_change=function(x,lag=1){
  n=length(x)
  if (n < 2) return(rep(NA, n))
  pchange = c((x[(1+lag):n]-x[1:(n-lag)])/x[1:(n-lag)],NA)
  return(pchange)
}
```


calculating daily returns for NYSE and merging sectors and industry data. 
```{r}

load("Data/NYSE_Stock_Data.Rda")
Yearly_returns <- 
  NYSE %>% 
  arrange(company, date) %>%
  group_by(company) %>%
  mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(company, year) %>%
  summarise(yearly_return = prod(1 + daily_return) - 1, ndays = n()) 
  

NYSE_companies <- read.csv("Data/NYSE_companylist.csv", stringsAsFactors = FALSE, na.strings = "n/a")

Yearly_returns <-  
  Yearly_returns %>%
  left_join(NYSE_companies %>% select(company = Symbol, market_cap_2015 = MarketCap, Sector, Industry,IPOyear,Name)) 

  Yearly_returns=Yearly_returns[order(Yearly_returns$yearly_return,decreasing=TRUE),]
  Yearly_returns=Yearly_returns[order(Yearly_returns$year,decreasing=TRUE),]
  NYSE_Y_Returns=subset(Yearly_returns,! is.na(Yearly_returns$yearly_return))
  write.csv(NYSE_Y_Returns,file="NYSE_Y_returns.csv")

Yearly_returns1 <- 
  Yearly_returns %>%
  group_by(year) %>%
  mutate(top_10 = percent_rank(yearly_return) >= .90)  

Table_1 <- 
  Yearly_returns1 %>%
  group_by(Industry, year, top_10) %>%
  summarize(count = n()) %>%
  spread(value = count, key = top_10, fill = 0) %>%
  rename(bottom_90 = `FALSE`, top_10 = `TRUE`) %>% .[,-5] %>%
  mutate(proportion = top_10 / (bottom_90 + top_10)) %>%
  arrange(year, proportion)


#NYSE_sectors=merge(NYSE,companies,by.x=7,by.y=1)
#NYSE_sectors=NYSE_sectors[order(NYSE_sectors$company,decreasing = FALSE),]
#NYSE_sectors$daily_return=percentage_change(NYSE_sectors$adj_close,lag=1)
#NYSE_daily_returns=NYSE_daily_returns[is.finite(NYSE_daily_returns)]
#NYSE_sectors=NYSE_sectors[-c(nrow(NYSE_sectors))]
#NYSE_sectors$daily_returns=NYSE_daily_returns
#save(NYSE_sectors, file = "NYSE_Returns_Data.Rda")
```

# calculating daily returns for NASDAQ and merging sectors and industry data. 
```{r}
load("Data/NASDAQ_Stock_Data.Rda")
Yearly_returns <- 
  NASDAQ %>% 
  arrange(company, date) %>%
  group_by(company) %>%
  mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(company, year) %>%
  summarise(yearly_return = prod(1 + daily_return) - 1, ndays = n()) 
  

NASDAQ_companies <- read.csv("Data/NASDAQ_companylist.csv", stringsAsFactors = FALSE, na.strings = "n/a")

Yearly_returns <- 
  Yearly_returns %>%
  left_join(NASDAQ_companies %>% select(company = Symbol, market_cap_2015 = MarketCap, Sector, industry,IPOyear,Name)) 

  Yearly_returns=Yearly_returns[order(Yearly_returns$yearly_return,decreasing=TRUE),]
  Yearly_returns=Yearly_returns[order(Yearly_returns$year,decreasing=TRUE),]
  NASDAQ_Y_Returns=subset(Yearly_returns,! is.na(Yearly_returns$yearly_return))
  NASDAQ_Y_Returns=merge(NASDAQ_Y_Returns,Market_Return,by.x=2,by.y=1)
 # write.csv(NASDAQ_Y_Returns,file="NASDAQ_Y_returns.csv")
  
#load("~/Desktop/Honors-/NASDAQ_Stock_Data.Rda")
#NASDAQ_companies <- read.csv("NASDAQ_companylist.csv", stringsAsFactors = FALSE, na.strings = "n/a")
#NASDAQ_sectors=merge(NASDAQ,NASDAQ_companies,by.x=7,by.y=1)

#NASDAQ_sectors=NASDAQ_sectors[order(NASDAQ_sectors$date,decreasing = FALSE),]

#NASDAQ_daily_returns=percentage_change(NASDAQ_sectors$adj_close,lag=1)
#NASDAQ_daily_returns=NASDAQ_daily_returns[is.finite(NASDAQ_daily_returns)]
#NASDAQ_sectors$daily_returns=NASDAQ_daily_returns
#save(NASDAQ_sectors, file = "NASDAQ_Returns_Data.Rda")
```

# calculating daily returns for SP_500 and merging sectors and industry data. 
```{r}
load("Data/SP_500_Stock_Data.Rda")
Yearly_returns <- 
  SP_500 %>% 
  arrange(company, date) %>%
  group_by(company) %>%
  mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(company, year) %>%
  summarise(yearly_return = prod(1 + daily_return) - 1, ndays = n()) 
  

SP_500_companies <- read.csv("Data/S&P 500_companylist.csv", stringsAsFactors = FALSE, na.strings = "n/a")

Yearly_returns <- 
  Yearly_returns %>%
  left_join(SP_500_companies %>% select(company = Symbol, Sector,Name)) 

  Yearly_returns=Yearly_returns[order(Yearly_returns$yearly_return,decreasing=TRUE),]
  Yearly_returns=Yearly_returns[order(Yearly_returns$year,decreasing=TRUE),]
  SP_Y_Returns=subset(Yearly_returns,! is.na(Yearly_returns$yearly_return))
  SP_Y_Returns=merge(SP_Y_Returns,Market_Return,by.x=2,by.y=1)
  SP_Y_Returns=merge(SP_Y_Returns,MarketCap,by=c("company","year"))
  
  SP_Y_Returns$market_cap=as.numeric(SP_Y_Returns$market_cap)
  
  Total_Market_Cap=aggregate(market_cap ~ year, SP_Y_Returns, FUN=sum)
  Total_Market_Cap=rename(Total_Market_Cap,total_market_cap=`market_cap`)
  SP_Y_Returns=merge(SP_Y_Returns,Total_Market_Cap,by=c("year"))
  
  SP_Y_Returns=SP_Y_Returns[order(SP_Y_Returns$market_cap,decreasing=TRUE),]
  SP_Y_Returns=SP_Y_Returns[order(SP_Y_Returns$year,decreasing=TRUE),]
  
  SP_Y_Returns$Market_Weight=SP_Y_Returns$market_cap/SP_Y_Returns$total_market_cap
  
  SP_Y_Returns$Name.y=NULL
  SP_Y_Returns$Sector.y=NULL
  SP_Y_Returns$id=NULL
  SP_Y_Returns$ndays=NULL
  SP_Y_Returns=rename(SP_Y_Returns,Sector=`Sector.x`,Name=`Name.x`)
  #x=mutate(SP_Y_Returns,top_10 = percent_rank(Market_Weight) >= .90)
  #write.csv(SP_Y_Returns,file="SP500_Y_returns.csv")

   ##############
  Yearly_returns1 <- 
  SP_Y_Returns %>%
  group_by(year) %>%
  mutate(top_10 = percent_rank(yearly_return) >= .90)  
  
  
#SP_companies <- read.csv("S&P 500_companylist.csv", stringsAsFactors = FALSE, na.strings = "n/a")
#SP_sectors=merge(SP_500,companies,by.x=7,by.y=1)
#SP_sectors=SP_sectors[order(SP_sectors$date,decreasing = FALSE),]
#SP_daily_returns=percentage_change(SP_sectors$adj_close,lag=1)
#SP_sectors$daily_returns=SP_daily_returns
#save(SP_sectors, file = "SP_500_Returns_Data.Rda")
```

# Market Return as SP_500 Index return
```{r}
SP_500_Index=read.csv("Data/S&P500 INDEX.csv", stringsAsFactors = FALSE, na.strings = "n/a")
SP_Y_Index <- 
  SP_500_Index[order(SP_500_Index$Date,decreasing = FALSE),] %>% 
  mutate(daily_return = percentage_change(Adj.Close, lag = 1)) %>%
  mutate(year = lubridate::year(Date)) %>%
  group_by(year) %>%
  summarise(market_return = prod(1 + daily_return) - 1, ndays = n()) 
  Market_Return=subset(SP_Y_Index,! is.na(SP_Y_Index$market_return))
  Market_Return=rename(Market_Return, days_per_year= `ndays`)
```

Market Cap Data
```{r}
SP_marketCap <- read.csv("~/Desktop/S&P marketCap.csv", stringsAsFactors = FALSE, na.strings = "n/a", header=TRUE)


MarketCap=reshape(SP_marketCap,varying=c("X1987","X1988","X1989","X1990","X1991","X1992","X1993","X1994","X1995","X1996","X1997","X1998","X1999","X2000","X2001","X2002","X2003","X2004","X2005","X2006","X2007","X2008","X2009","X2010","X2011","X2012","X2013","X2014","X2015"),v.names="market_cap",timevar = "year",times=c("1987","1988","1989","1990","1991","1992","1993","1994","1995","1996","1997","1998","1999","2000","2001","2002","2003","2004","2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015"),direction = "long")
MarketCap=MarketCap[order(MarketCap$company,decreasing = FALSE),]
MarketCap=subset(MarketCap,market_cap != "N/A")
```


```{r}

#"Advance_decline Line calculation " " AD= (#winning companies-#of losing companies) +AD(t-1)"

# Total number of companies per year 
NYSE_Companies_per_year=as.data.frame(table(NYSE_Y_Returns$year))
NYSE_Companies_per_year=rename(NYSE_Companies_per_year,year = `Var1`, total_comps = `Freq`)

# Number of companies with yearly return>0 per year
NYSE_Winning_comps=as.data.frame(table(subset(NYSE_Y_Returns,yearly_return>0)$year))
NYSE_Winning_comps=rename(NYSE_Winning_comps,year = `Var1`, winning = `Freq`)

# Number of companies with yearly return>0 per year
NYSE_Losing_comps=as.data.frame(table(subset(NYSE_Y_Returns,yearly_return<0)$year))
NYSE_Losing_comps=rename(NYSE_Losing_comps,year = `Var1`, losing = `Freq`)

# Merging above tables and summarizing it to create data for AD calculations 
AD_line_data=merge(NYSE_Winning_comps,NYSE_Losing_comps,by.x=1, by.y =1)
AD_line_data$total=NYSE_Companies_per_year$total_comps
AD_line_data$percWin=AD_line_data$winning/AD_line_data$total
AD_line_data$percLose=AD_line_data$losing/AD_line_data$total
AD_line_data$WinLoseDiff=AD_line_data$winning-AD_line_data$losing

# Calculating AD_line 
AD_line_data$AD_line[1]=AD_line_data$WinLoseDiff[1]
for(i in 2:nrow(AD_line_data)){
  AD_line_data$AD_line[i]=AD_line_data$WinLoseDiff[i]+AD_line_data$AD_line[i-1]
}
plot(AD_line_data$year,AD_line_data$AD_line,main="Advance/Decline Line",xlab="Years",Ylab="AD_line(#win-#lost+AD(t-1) *t=Time",type="l",col="red")
lines(AD_line_data$year,AD_line_data$AD_line,type="l",col="red")

plot(AD_line_data$year,AD_line_data$WinLoseDiff,main="difference between the number of winning and losing companies",xlab="Years",Ylab="win-lose")
lines(AD_line_data$year,AD_line_data$WinLoseDiff,type="l",col="red")

write.csv(AD_line_data,file="NYSE_AD_Line_data.csv")
```


 #S&P Tech Companies with higher return than industry average
```{r}
#"Advance_decline Line calculation " " AD= (#winning companies-#of losing companies) +AD(t-1)"

# Total number of companies per year 
SP_Companies_per_year=as.data.frame(table(SP_Y_Returns$year))
SP_Companies_per_year=rename(SP_Companies_per_year,year = `Var1`, total_winning = `Freq`)



# Number of companies with yearly return>0 per year
Tech_comps=as.data.frame((subset(SP_Y_Returns,Sector=="Information Technology" | Sector=="Technology")))
techPerYear=as.data.frame(table(Tech_comps$year))
techPerYear$total=SP_Companies_per_year$total_winning
techPerYear$techPerc=techPerYear$Freq/techPerYear$total
techPerYear=rename(techPerYear,year=`Var1`, tech=`Freq`)

Tech_win=as.data.frame(table(subset(Tech_comps,yearly_return>mean(yearly_return))$year))
Tech_win=rename(Tech_win,year = `Var1`, winning = `Freq`)

# Number of companies with yearly return>0 per year
SP_Losing_comps=as.data.frame(table(subset(Tech_comps,yearly_return<mean(yearly_return))$year))
SP_Losing_comps=rename(SP_Losing_comps,year = `Var1`, losing = `Freq`)

# Merging above tables and summarizing it to create data for AD calculations 
AD_line_data=merge(Tech_win,SP_Losing_comps,by.x=1, by.y =1)
#AD_line_data$total=SP_Companies_per_year$total_winning
#AD_line_data$percWin=AD_line_data$winning/AD_line_data$total
#AD_line_data$percLose=AD_line_data$losing/AD_line_data$total
AD_line_data$WinLoseDiff=AD_line_data$winning-AD_line_data$losing

# Calculating AD_line 
AD_line_data$AD_line[1]=AD_line_data$WinLoseDiff[1]
for(i in 2:nrow(AD_line_data)){
  AD_line_data$AD_line[i]=AD_line_data$WinLoseDiff[i]+AD_line_data$AD_line[i-1]
}
plot(AD_line_data$year,AD_line_data$AD_line,main="Tech Industry Advance/Decline Line",xlab="Years",Ylab="AD_line(#win-#lost+AD(t-1) *t=Time",type="l",col="red")
lines(AD_line_data$year,AD_line_data$AD_line,type="l",col="red")

plot(AD_line_data$year,AD_line_data$WinLoseDiff,main="difference between winning and losing tech companies ",xlab="Years",Ylab="win-lose")
lines(AD_line_data$year,AD_line_data$WinLoseDiff,type="l",col="red")

plot(AD_line_data$year,Market_Return$market_return,type="l",col="green")
lines(AD_line_data$year,SP_Y_Returns$market_return,type="l",col="green")
write.csv(AD_line_data,file="Tech_AD_Line_data.csv")
```

Companies beating the market  
```{r}
SP_Companies_per_year=as.data.frame(table(SP_Y_Returns$year))
SP_Companies_per_year=rename(SP_Companies_per_year,year = `Var1`, companies = `Freq`)

beat_the_market=as.data.frame(table(subset(SP_Y_Returns,yearly_return>market_return)$year))
beat_the_market=rename(beat_the_market, year = `Var1`, winning_companies = `Freq`)

less_than_market=as.data.frame(table(subset(SP_Y_Returns,yearly_return<market_return)$year))
less_than_market=rename(less_than_market,year = `Var1`, losing_companies = `Freq`)

line_data=merge(beat_the_market,less_than_market,by.x=1, by.y =1)
line_data$total=SP_Companies_per_year$companies
line_data$percWin=line_data$winning_companies/line_data$total
line_data$percLose=line_data$losing_companies/line_data$total
line_data$WinLoseDiff=line_data$winning_companies-line_data$losing_companies


```



#Junk Code
NYSE Data Summary
```{r}
# Calculating Annual Returns by Summing Daily Returns per year 
Returns <- 
  NYSE %>% 
  arrange(company, date) %>%
  group_by(company) %>%
  mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(company, year) %>%
  summarise(yearly_return = prod(1 + daily_return) - 1, ndays = n()) %>%
  Returns=Returns[order(Returns$yearly_return,decreasing=TRUE),] %>%
  Returns=Returns[order(Returns$year,decreasing=TRUE),]
 # calculating 5-year return
number_of_years=5
counter=0
for(i in (1986:2015)){
  data=Returns[order(Returns$company),]
  group_by(data,company)
  compTable=as.data.frame(table(data$company))
  compTable=rename(compTable,company= `Var1`, company_years = `Freq`)
  data=merge(data,compTable,by.x=1,by.y=1)
  
  first5=subset(Returns,Returns$year<1991)
  fiveYear_Return <-
    first5=first5[order(first5$company),] %>%
    group_by(company,year) %>%
    summarise(fiveYear_Return=sum(yearly_returns))
    
  while(counter<5){
    
  }
}
  



#"Number of companies with annual returns adding up to 10% of Market Returns"
companies=c()
year=c()
percent=0.1
for(i in c(1987:2015)){
  n=0
  number_of_companies=0
  year=c(year,i)
  term=which(SP_Y_Returns$year==i) # Returns the list of indexs of the year i
  term=term[1]
  while(n<percent){
    n=n+SP_Y_Returns$Market_Weight[term]
    print(n)
    number_of_companies=number_of_companies+1
    print(number_of_companies)
    term=term+1
  }
  companies=c(companies,number_of_companies)
}
comp10=data.frame(companies,year)
comp10=rename(comp10,top10=`companies`)


comp20=data.frame(companies,year)
comp20=rename(comp20,top20=`companies`)

total_companies=as.data.frame(table(SP_Y_Returns$year))
total_companies=rename(total_companies,year=`Var1`,companies=`Freq`)

compNum=merge(comp10,comp20)

marketShare=merge(compNum,total_companies)
marketShare$top10_ratio=marketShare$top10/marketShare$companies
marketShare$top20_ratio=marketShare$top20/marketShare$companies

# get company info using the indexes in comp
topComps=c()
companies=c()
for(i in 1:length(comp10$year)){
    print(i)
    print(comp10$year[i])
    term=which(SP_Y_Returns$year==comp10$year[i])
    print(comp10$top10[i])
    topComps=SP_Y_Returns[term[1:comp10$top10[i]],]
    companies=rbind(companies,topComps)
    }
  

  


```

```{r}

```

