
Install needed packages 
```{r include = TRUE}
library(dplyr)
library(tidyr)
```

function to calculate percentage change (return)
```{r}
percentage_change=function(x,lag=1){
  n=length(x)
  if (n < 2) return(rep(NA, n))
  pchange = c((x[(1+lag):n]-x[1:(n-lag)])/x[1:(n-lag)],NA)
  return(pchange)
}
```


# Market Return 
"SP_500 Index return"
```{r}
market_R_filePath="Data/S&P500 INDEX.csv"
MarketReturn_Data=function(filePath){
  
  SP_500_Index=read.csv(filePath, stringsAsFactors = FALSE, na.strings = "n/a")
  SP_Y_Index <- 
    SP_500_Index[order(SP_500_Index$Date,decreasing = FALSE),] %>% 
    mutate(daily_return = percentage_change(Adj.Close, lag = 1)) %>%
    mutate(year = lubridate::year(Date)) %>%
    group_by(year) %>%
    summarise(market_return = prod(1 + daily_return) - 1, ndays = n()) 
  Market_Return=subset(SP_Y_Index,! is.na(SP_Y_Index$market_return))
  Market_Return=rename(Market_Return, days_per_year= `ndays`)
}

```


#Market Cap Data
This function takes market cap data and reshapes it
```{r}
MarketCap_filepath="Data/S&P marketCap.csv"
MarketCap_Data=function(filePath){
  SP_marketCap <- read.csv(filePath, stringsAsFactors = FALSE, na.strings = "n/a", header=TRUE)
  
  
  MarketCap=reshape(SP_marketCap,varying=c("X1987","X1988","X1989","X1990","X1991","X1992","X1993","X1994","X1995","X1996","X1997","X1998","X1999","X2000","X2001","X2002","X2003","X2004","X2005","X2006","X2007","X2008","X2009","X2010","X2011","X2012","X2013","X2014","X2015"),v.names="market_cap",timevar = "year",times=c("1987","1988","1989","1990","1991","1992","1993","1994","1995","1996","1997","1998","1999","2000","2001","2002","2003","2004","2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015"),direction = "long")
  MarketCap=MarketCap[order(MarketCap$company,decreasing = FALSE),]
  MarketCap=subset(MarketCap,market_cap != "N/A" & market_cap !="" )
  MarketCap$year=as.numeric(MarketCap$year)
  MarketCap
}
```

# Cleaning Main Downloaded Data
a. get Data
b.Calculate Annual return
c. merge with market cap and annual return datasets 
d. output is ranked by market Cap
```{r}
MainData_filepath="Data/SP_H.csv"
GetMain_Data=function(filePath){
  
SP_H=read.csv(filePath, stringsAsFactors = FALSE, na.strings = "n/a", header=TRUE)
Yearly_returns <- 
  subset(SP_H,SP_H$volume!=0) %>% 
  arrange(company, date) %>%
  group_by(company) %>%
  mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(company, year) %>%
  summarise(yearly_return = prod(1 + daily_return) - 1, ndays = n()) 

  Yearly_returns=Yearly_returns[order(Yearly_returns$yearly_return,decreasing=TRUE),]
  Yearly_returns=Yearly_returns[order(Yearly_returns$year,decreasing=TRUE),]
  SP_Y_H=subset(Yearly_returns,!is.na(Yearly_returns$yearly_return))
  SP_Y_H=subset(SP_Y_H,SP_Y_H$ndays>90)
#  Merging data SP Yearly Returns data with Market Returns and Market Cap Data.
  marketCap=MarketCap_Data(filePath=MarketCap_filepath)
  marketReturn=MarketReturn_Data(filePath = market_R_filePath)
  print(nrow(SP_Y_H))
   SP_Y_H=merge(SP_Y_H,marketReturn,by=c("year"))
   SP_Y_H=merge(SP_Y_H,marketCap,by=c("year","company"))
  
#  ordering by size and taking 246 comps baskets 
  SP_Y_H$market_cap=as.numeric(SP_Y_H$market_cap)
  SP_Y_H=SP_Y_H[order(SP_Y_H$market_cap, decreasing = TRUE),]
  SP_Y_H=SP_Y_H[order(SP_Y_H$year, decreasing = TRUE),]
}
```


Calculate total annual contribution (sum of abs individual contributions)
a. calculate contribution weights with no direction 
b. output is ranked by market contribution
```{r}
 TotalContribution=function(Data){
    annualContribution=aggregate(abs(contribution)~year,Data, FUN=sum)
    annualContribution=rename(annualContribution,Contribution_Y=`abs(contribution)`)
    Data=merge(Data,annualContribution,by=c("year"))
    Data$Contribution_W=abs(Data$contribution)/Data$Contribution_Y
    Data=Data[order(Data$contribution,decreasing = TRUE),]
    Data=Data[order(Data$year,decreasing = TRUE),]
    Data
  }
```


This function calculates the following:
a. total market cap 
b. companies weight 
c. individual contribution 
d.calls TotalContribution funcion 
e.output is ranked by market contribution
```{r}
  TotalCap=function(Data){
    Total_Market_Cap=aggregate(market_cap ~ year, Data, FUN=sum)
    Total_Market_Cap=rename(Total_Market_Cap,total_market_cap=`market_cap`)
    Data=merge(Data,Total_Market_Cap,by=c("year"))
    Data$Market_Weight= Data$market_cap/ Data$total_market_cap
    Data$contribution=Data$Market_Weight* Data$yearly_return
    annualContribution=TotalContribution(Data)
    annualContribution
  }
```

This function takes in cleaned main_data and creates equal baskets of companies per year, ranked by size
a. it calls on all previous function and outputs the final data set 
b. final dataset is ranked by contribution 

```{r}
  
  getTop_n=function(data,n){
    Comps=c()
    company=c()
    years=as.data.frame(table(data$year))
    years=rename(years,year=`Var1`)
    for(i in 1:length(years$year)){
      term=which(data$year==years$year[i])
      Comps=data[term[1:n],]
      company=rbind(company,Comps)
    }
    Top_n=company[order(company$year,decreasing=TRUE),]
    #add total Market Cap
   
    TotalMarket_Cap=TotalCap(Top_n)
    internet=InternetComps(TotalMarket_Cap,companyList)
    internet
  }
```

Add Market Cap Percentage Growth
```{r}
Cap_Growth=function(data){
  cap=data %>% 
  arrange(company,year) %>%
  group_by(company) %>%
  mutate(Cap_growth= percentage_change(market_cap, lag = 1)) 
  cap=cap[order(cap$Cap_growth,decreasing=TRUE),]
  cap=cap[order(cap$year,decreasing=TRUE),]
  cap
}
```


```{r}

MultipleYearReturn=function(Nyears,filePath){
  library(quantmod)
  SP_H=read.csv(filePath, stringsAsFactors = FALSE, na.strings = "n/a", header=TRUE)
  za <- 
    subset(SP_H,SP_H$volume!=0)%>% 
    arrange(company, date) %>%
    group_by(company) %>%
    mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
    mutate(year = lubridate::year(date)) %>%
    group_by(company, year)
  sa=as.data.frame(table(za$year,za$company))
  sa=subset(sa,sa$Freq>0)
  sa$cumSum=cumsum(sa$Freq)
  
  d<-za[sa$cumSum,]
  multiple_Y_Returns=c()
  list1=as.data.frame(table(d$company))
  list1=rename(list1,company=`Var1`,years=`Freq`)
  list1=subset(list1,years>Nyears)
  for(i in 1:nrow(list1)){
    temp=subset(d,d$company==list1$company[i])
    years=list1$years[i]
    returns=as.data.frame(Delt(temp$adj_close,k=Nyears,type="arithmetic"))
    temp1=cbind(returns,temp$year)
    temp1=rename(temp1,year=`temp$year`)
    temp2=merge(temp1,temp,by=c("year"))
    multiple_Y_Returns=rbind(temp2,multiple_Y_Returns)
  }
  marketCap=MarketCap_Data(filePath=MarketCap_filepath)
  marketReturn=MarketReturn_Data(filePath = market_R_filePath)
  multiple_Y_Returns=merge(multiple_Y_Returns,marketReturn,by=c("year"))
  multiple_Y_Returns=merge(multiple_Y_Returns,marketCap,by=c("year","company"))
  multiple_Y_Returns$market_cap=as.numeric(multiple_Y_Returns$market_cap)
  multiple_Y_Returns=rename(multiple_Y_Returns, yearly_return=`Delt.3.arithmetic`)
  multiple_Y_Returns=subset(multiple_Y_Returns,! is.na(multiple_Y_Returns$yearly_return))
  multiple_Y_Returns=multiple_Y_Returns[order(multiple_Y_Returns$market_cap, decreasing = TRUE),]
  multiple_Y_Returns=multiple_Y_Returns[order(multiple_Y_Returns$year, decreasing = TRUE),]
  #multiple_Y_Returns= getTop_n(multiple_Y_Returns,236)
  
  multiple_Y_Returns
}
  
  
#  ordering by size and taking 246 comps baskets 
 

#multiple_Y_Returns=subset(multiple_Y_Returns,! is.na(multiple_Y_Returns$Delt.5.arithmetic))



```

