---
title: "Regression analysis"
output: html_document
---


Get Data
```{r}
mainData=GetMain_Data(filePath = MainData_filepath)
Top_246=getTop_n(data=mainData,n=246)

RegressionData=PrepareSurvivalData(25,Top_246,2000,recessionData)

threeYear=MultipleYearReturn(3,MainData_filepath)
threeYear=getTop_n(threeYear,236)
fiveYear=MultipleYearReturn(5,MainData_filepath)
fiveYear=getTop_n(fiveYear,236)
```


Survival Regression Data 
```{r}
# Temporal Regressions
# period 1987-1995
oneYearReturn=subset(Top_246,Top_246$year>=2009 & Top_246$year<=2015)
threeYearReturn=subset(threeYear,threeYear$year>=2009 & threeYear$year<=2015)
fiveYearReturn=subset(fiveYear,fiveYear$year>=2009 & fiveYear$year<=2015)

# run regressions function 

timePeriodReg=function(Data,formula){
  #RegData=Cap_Growth(Data)
  RegData=Internet_T(Data,1995)
  RegData=recession_T(RegData,recessionData)
  #RegData=subset(RegData, ! is.na(RegData$Cap_growth))
  RegData=InternetComps(RegData,companyList)
  summary(lm(formula,data=RegData))
}

```


```{r}
library(survival)
CoxSnell = function(cs,status,xlim=NULL,ylim=NULL) {
kmcs = survfit(Surv(cs,status)~1)$surv
plot(log(-log(kmcs))~unique(sort(log(cs))),xlab="log(Cox-Snell)",ylab="log(-log(S(Cox-Snell)))",xlim=xlim,ylim=ylim)
abline(0,1,col='red') }

#CS = -log( 1 - mod1(Melanoma$Days,1/exp(9.469850975-0.001566502*Melanoma$Thickness ) ) )

```
```

```{r}

mod=lm(formula=contribution~ recession+ Sector+total_market_cap, data= InternetComps(Top_246,companyList))
mod1=coxph(Surv(Freq,Status)~Sector, data=Survival1Year)
mod1
plot(survfit(mod1))
```

LASSO Regression 
```{r}
y=InternetComps(Top_246,companyList)

y=subset(Top_246,Top_246$year<=2015 & Top_246$year>=2010)

x=model.matrix(contribution~Sector+company*year+InternetCompany, data=y)
foo=cv.glmnet(x,y$contribution,alpha=1)
predict(foo,s=foo$lambda.min,exact=T,type="coefficients")
```

Panel Data Models
```{r}

library(plm)
internetDummy=InternetComps(Top_246,companyList)
recession_Data=recession_T(internetDummy,recessionData)

#R_Data=recession_Data[order(recession_Data$year,decreasing = TRUE),] 
#recession_Data=recession_Data[order(recession_Data$company,decreasing = TRUE),]

#attach(recession_Data)
Y=cbind(contribution)
X=cbind(Sector,year,InternetCompany,total_market_cap,recession)

pData=plm.data(threeYear,index=c("company","year"))
pData5=plm.data(fiveYear,index=c("company","year"))

pooling=plm(contribution~Sector+year+InternetCompany,data=pData5,model="pooling")

firstDiff=plm(contribution~Sector+year+InternetCompany,data=pData,model="fd")
fixed=plm(contribution~Sector+year+InternetCompany,data=pData,model="within")
random=plm(contribution~Sector+year+InternetCompany,data=pData,model="random")
between=plm(contribution~Sector+year+InternetCompany,data=pData,model="between")
```

