
 Market Return as SP_500 Index return
```{r}
SP_500_Index=read.csv("Data/S&P500 INDEX.csv", stringsAsFactors = FALSE, na.strings = "n/a")
SP_Y_Index <- 
  SP_500_Index[order(SP_500_Index$Date,decreasing = FALSE),] %>% 
  mutate(daily_return = percentage_change(Adj.Close, lag = 1)) %>%
  mutate(year = lubridate::year(Date)) %>%
  group_by(year) %>%
  summarise(market_return = prod(1 + daily_return) - 1, ndays = n()) 
  Market_Return=subset(SP_Y_Index,! is.na(SP_Y_Index$market_return))
  Market_Return=rename(Market_Return, days_per_year= `ndays`)
```

Grouping by 10% of total companies and measuring group contribution 
```{r}
SP_Y_H=read.csv("SP_Y_H.csv")
SP_Y_H=SP_Y_H[order(SP_Y_H$contribution,decreasing=TRUE),]
SP_Y_H=SP_Y_H[order(SP_Y_H$year,decreasing=TRUE),]
SP_C_Weigh<-
  SP_Y_H %>%
  group_by(year) %>%
  summarise(annualContribution=sum(contribution))
SP_Y_H=merge(SP_Y_H,SP_C_Weigh,by.x="year",by.y = "year")

ss=as.data.frame(table(SP_Y_H$year))
xx=SP_Y_H
percentage=0.1
newData=c()
for(i in 1:nrow(ss)){
  numberOfC=ceiling(percentage*ss$Freq[i])
  my_data=xx[which(xx$year==ss$Var1[i]),]
  limitx=1
  limity=numberOfC
  n=1
  while((ss$Freq[i]-limity)>numberOfC){
    temp=my_data[limitx:limity,]
    limitx=limity+1
    limity=limity+numberOfC
    chunkContribution=sum(temp$contribution)
    year=1986+as.numeric(ss$Var1[i])
    data=c(year,n,chunkContribution,nrow(temp))
    n=n+1
    newData=rbind(newData,data)
  }
    temp=my_data[limitx:ss$Freq[i],]
    chunkContribution=sum(temp$contribution)
    year=1986+as.numeric(ss$Var1[i])
    data=c(year,n,chunkContribution,nrow(temp))
    n=n+1
    newData=rbind(newData,data)
}
newData=as.data.frame(newData)
newData=rename(newData,year=`V1`,ChunkNum=`V2`,ChunkContribution=`V3`,Chunksize=`V4`)

totalContribution=SP_Y_H[,c("year", "annualContribution")]
totalContribution=unique(totalContribution[c("year", "annualContribution")])
ContributionData=merge(newData,totalContribution,by.x="year",by.y="year")
ContributionData$ChunkWeight=ContributionData$ChunkContribution/abs(ContributionData$annualContribution)
#write.csv(ContributionData,file="SP_Y_H_Contribution.csv")


# GraphsData
Chunk1=subset(ContributionData,ChunkNum==1)
Chunk2=subset(ContributionData,ChunkNum==2)
Chunk3=subset(ContributionData,ChunkNum==3)
Chunk4=subset(ContributionData,ChunkNum==4)
Chunk5=subset(ContributionData,ChunkNum==5)
Chunk6=subset(ContributionData,ChunkNum==6)
Chunk7=subset(ContributionData,ChunkNum==7)
Chunk8=subset(ContributionData,ChunkNum==8)
Chunk9=subset(ContributionData,ChunkNum==9)

par(mfrow=c(2,2))
"Market Contribution by Chunk"
"Top(10%,20%)-Bottom(10%,20%) Chunks and Market Contribution"


plot(Chunk1$year,Chunk1$ChunkWeight,col="blue",main="Top(10%) Bottom(10%) Chunks and Market Contribution", sub="Top10%=Blue , Bottom10%=Red",ylim=c(-4,4),xlab="Years", ylab="Chunk Contribution")
lines(Chunk1$year,Chunk1$ChunkWeight,col="blue")
lines(Chunk2$year,Chunk2$ChunkWeight,col="green")
lines(Chunk3$year,Chunk3$ChunkWeight,col="yellow")
lines(Chunk4$year,Chunk4$ChunkWeight,col="brown")
lines(Chunk5$year,Chunk5$ChunkWeight,col="pink")
lines(Chunk6$year,Chunk6$ChunkWeight,col="mediumseagreen")
lines(Chunk9$year,Chunk7$ChunkWeight,col="midnightblue")
lines(Chunk8$year,Chunk8$ChunkWeight,col="olivedrab")
lines(Chunk9$year,Chunk9$ChunkWeight,col="red")

t

```

calculating multiple years return
```{r}
za <- 
  SP_500 %>% 
  arrange(company, date) %>%
  group_by(company) %>%
  mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(company, year)
  sa=as.data.frame(table(za$year,za$company))
  sa=subset(sa,sa$Freq>0)
  sa$cumSum=cumsum(sa$Freq)
                 
d<-za[sa$cumSum,]
multiple_Y_Returns=c()
list1=as.data.frame(table(d$company))
list1=rename(list1,company=`Var1`,years=`Freq`)
list1=subset(list1,years>3)
for(i in 1:nrow(list1)){
  temp=subset(d,d$company==list1$company[i])
  print(i)
  years=list1$years[i]
  #if(years<=3){
   # returns=as.data.frame(Delt(temp$adj_close,k=,type="arithmetic"))
  #}
  #else{
   returns=as.data.frame(Delt(temp$adj_close,k=3,type="arithmetic"))
  #} 
  temp1=cbind(returns,temp$year)
  temp1=rename(temp1,year=`temp$year`)
  temp2=merge(temp1,temp,by.x="year",by.y="year")
  multiple_Y_Returns=rbind(temp2,multiple_Y_Returns)
}
multiple_Y_Returns=merge(multiple_Y_Returns,SP_500_companies,by.x="company",by.y="Symbol")
multiple_Y_Returns=subset(multiple_Y_Returns,! is.na(multiple_Y_Returns$Delt.3.arithmetic))
multiple_Y_Returns=multiple_Y_Returns[order(multiple_Y_Returns$Delt.3.arithmetic,decreasing = TRUE),]
multiple_Y_Returns=multiple_Y_Returns[order(multiple_Y_Returns$year,decreasing = TRUE),]
Three_Y_Return=multiple_Y_Returns[,c(1,2,3,9,12,13)]
Three_Y_Return=merge(Three_Y_Return,Market_Return,by=("year"))
Three_Y_Return=merge(Three_Y_Return,MarketCap,by=c("company","year"))
Three_Y_Return$market_cap=as.numeric(Three_Y_Return$market_cap)
Three_Y_Return=Three_Y_Return[,c(1,2,3,4,5,6,7,8,11)]
Three_Y_Return=merge(Three_Y_Return,Total_Market_Cap,by=c("year"))
Three_Y_Return$Market_Weight=Three_Y_Return$market_cap/Three_Y_Return$total_market_cap
Three_Y_Return$contribution=Three_Y_Return$Market_Weight*Three_Y_Return$Delt.3.arithmetic

```


Market Cap Data
```{r}
SP_marketCap <- read.csv("Data/S&P marketCap.csv", stringsAsFactors = FALSE, na.strings = "n/a", header=TRUE)


MarketCap=reshape(SP_marketCap,varying=c("X1987","X1988","X1989","X1990","X1991","X1992","X1993","X1994","X1995","X1996","X1997","X1998","X1999","X2000","X2001","X2002","X2003","X2004","X2005","X2006","X2007","X2008","X2009","X2010","X2011","X2012","X2013","X2014","X2015"),v.names="market_cap",timevar = "year",times=c("1987","1988","1989","1990","1991","1992","1993","1994","1995","1996","1997","1998","1999","2000","2001","2002","2003","2004","2005","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015"),direction = "long")
MarketCap=MarketCap[order(MarketCap$company,decreasing = FALSE),]
MarketCap=subset(MarketCap,market_cap != "N/A")
```

calculating daily returns for SP_500 and merging market cap and returns data.
```{r}
SP_H1=load("Data/SP_H_Data.Rda")
Yearly_returns <- 
  subset(SP_H,SP_H$volume!=0) %>% 
  arrange(company, date) %>%
  group_by(company) %>%
  mutate(daily_return = percentage_change(adj_close, lag = 1)) %>%
  mutate(year = lubridate::year(date)) %>%
  group_by(company, year) %>%
  summarise(yearly_return = prod(1 + daily_return) - 1, ndays = n()) 
  
SP_500_companies <- read.csv("Data/S&P 500_companylist.csv", stringsAsFactors = FALSE, na.strings = "n/a")

Yearly_returns <- 
  Yearly_returns %>%
  left_join(MarketCap %>% select(company,Sector,Name,market_cap)) 

  Yearly_returns=Yearly_returns[order(Yearly_returns$yearly_return,decreasing=TRUE),]
  Yearly_returns=Yearly_returns[order(Yearly_returns$year,decreasing=TRUE),]
  SP_Y_H=subset(Yearly_returns,!is.na(Yearly_returns$yearly_return))
  SP_Y_H=subset(SP_Y_H,SP_Y_H$ndays>90)
#  Merging data SP Yearly Returns data with Market Returns and Market Cap Data.
   SP_Y_H=merge(SP_Y_H,Market_Return,by.x=2,by.y=1)
   SP_Y_H=merge(SP_Y_H,MarketCap,by=c("company","year"))
  
#  Creating new variables 
  SP_Y_H$market_cap=as.numeric(SP_Y_H$market_cap)
  Total_Market_Cap=aggregate(market_cap ~ year, SP_Y_H, FUN=sum)
  Total_Market_Cap=rename(Total_Market_Cap,total_market_cap=`market_cap`)
  SP_Y_H=merge(SP_Y_H,Total_Market_Cap,by=c("year"))
  
 SP_Y_H=SP_Y_H[order(SP_Y_H$market_cap,decreasing=TRUE),]
  SP_Y_H=SP_Y_H[order(SP_Y_H$year,decreasing=TRUE),]
  SP_Y_H$Market_Weight=SP_Y_H$market_cap/SP_Y_H$total_market_cap
  SP_Y_H$contribution=SP_Y_H$Market_Weight*SP_Y_H$yearly_return
# Removing duplicate columns from data sets and renameing others. 
  SP_Y_H$Name.y=NULL
  SP_Y_H$Sector.y=NULL
  SP_Y_H$id=NULL
  SP_Y_H$ndays=NULL
  SP_Y_H=rename(SP_Y_H,Sector=`Sector.x`,Name=`Name.x`)
  
  write.csv(SP_Y_H,file="SP_Y_H.csv")

```

"Number of companies with Market Weight adding up to 10% of Market-cap"
```{r}
##
#list of technology companies 
TechComps=as.data.frame(subset(SP_Y_Returns,Sector=="Information Technology"|Sector=="Consumer Discretionary"))
##
companies=c()
year=c()
percent=0.4  # change as desired
for(i in c(1987:2015)){
  n=0
  number_of_companies=0
  year=c(year,i)
  term=which(SP_Y_Returns$year==i) # Returns the list of indexs of the year i
  term=term[1]
  while(n<percent){
    n=n+SP_Y_Returns$Market_Weight[term]
    print(n)
    number_of_companies=number_of_companies+1
    print(number_of_companies)
    term=term+1
  }
  companies=c(companies,number_of_companies)
}


Top10=data.frame(companies,year)
Top10=rename(Top10,top10=`companies`)

# change percent to 0.2 then re run the loop and the below code.
Top20=data.frame(companies,year)
Top20=rename(Top20,top20=`companies`)
# change percent to 0.3 then re run the loop and the below code.
Top30=data.frame(companies,year)
Top30=rename(Top30,top30=`companies`)
# change percent to 0.4 then re run the loop and the below code.
Top40=data.frame(companies,year)
Top40=rename(Top40,top40=`companies`)

# Merging top10 and top20 and calcualting their percentage out of the total index
total_companies=as.data.frame(table(SP_Y_Returns$year))
total_companies=rename(total_companies,year=`Var1`,companies=`Freq`)

TopComps=merge(TopComps,Top40)
marketShare=merge(TopComps,total_companies)
marketShare$top10_ratio=marketShare$top10/marketShare$companies
marketShare$top20_ratio=marketShare$top20/marketShare$companies
marketShare$top30_ratio=marketShare$top30/marketShare$companies
marketShare$top40_ratio=marketShare$top40/marketShare$companies


###########
#Graphs
plot(marketShare$year,marketShare$top20_ratio,type="l",col="green",ylim=c(0,0.08),main="Percentage of companies accounting for 10%,20%,30% and 40% of the market",sub="red=10%, green=20%, blue=30%, yellow=40%", xlab="Years", ylab="Percentage of companies")
lines(marketShare$year,marketShare$top30_ratio,type="l",col="blue")
lines(marketShare$year,marketShare$top10_ratio,type="l",col="red")
lines(marketShare$year,marketShare$top40_ratio,type="l",col="yellow")


plot(marketShare$year,marketShare$top20,type="l",col="green",ylim=c(0,40),main="number of companies accounting for 10%, 20% 30% and 40% of the market value over years",sub="red=10%, green=20%, blue=30%, yellow=40%", xlab="Years", ylab="number of companies")
lines(marketShare$year,marketShare$top30,type="l",col="blue")
lines(marketShare$year,marketShare$top10,type="l",col="red")
lines(marketShare$year,marketShare$top40,type="l",col="yellow")


```

list of companies adding up to 10% market share using Top10. "Use Top20 for top 20%"

```{r}
Comps=c()
company=c()
for(i in 1:length(Top40$year)){
    term=which(SP_Y_Returns$year==Top40$year[i])
    Comps=SP_Y_Returns[term[1:Top40$top40[i]],]
    company=rbind(company,Comps)
    }
Top40_Y=company[order(company$year,decreasing=TRUE),]  
View(Top40_Y)
write.csv(Top40_Y,file="S&P_Top40%.csv")

x=as.data.frame(table(Top10_Y$year,Top10_Y$company))
y=subset(x,x$Freq>0)


#Graphics Sectors in the top 10% over time 
sectors=as.data.frame(table(Top40_Y$Sector))
sectors_Y=as.data.frame(table(Top40_Y$Sector,Top40_Y$year))

# x1=subset(sectors_Y,sectors_Y$Var2=="Consumer Discretionary")
 x2=subset(sectors_Y,sectors_Y$Var1=="Consumer Staples")
 #x3=subset(sectors_Y,sectors_Y$Var1=="Energy")
 x4=subset(sectors_Y,sectors_Y$Var1=="Financials")
 x5=subset(sectors_Y,sectors_Y$Var1=="Health Care")
 #x6=subset(sectors_Y,sectors_Y$Var1=="Industrials")
 x7=subset(sectors_Y,sectors_Y$Var1=="Information Technology")
 #x8=subset(sectors_Y,sectors_Y$Var2=="Telecommunications Services")

par(mfrow=c(2,2))
plot(x1$Var1,x2$Freq,col="red",main="Consumer Staples in top 40% per year",ylim=c(0,7),xlab="Years", ylab="Number of companies")
lines(x1$Var1,x2$Freq,col="red")

plot(x1$Var1,x4$Freq,col="green",main="Financials in top 40% per year",ylim=c(0,7),xlab="Years", ylab="Number of companies")
lines(x1$Var1,x4$Freq,col="green")


plot(x1$Var1,x5$Freq,col="yellow",main="Health Care in top 40% per year",ylim=c(0,7),xlab="Years", ylab="Number of companies")
lines(x1$Var1,x5$Freq,col="yellow")

plot(x1$Var1,x7$Freq,col="blue",main="Information Technology in top 40% per year",ylim=c(0,11),xlab="Years", ylab="Number of companies")
lines(x1$Var1,x7$Freq,col="blue")


#lines(x1$Var1,x8$Freq,col="yellow")


# Get percentage of Technological companies compared to others
```


S&P Tech Companies with higher return than industry average
```{r}
#"Advance_decline Line calculation " " AD= (#winning companies-#of losing companies) +AD(t-1)"

# Total number of companies per year 
SP_Companies_per_year=as.data.frame(table(SP_Y_Returns$year))
SP_Companies_per_year=rename(SP_Companies_per_year,year = `Var1`, total_winning = `Freq`)



# Number of companies with yearly return>0 per year
Tech_comps=as.data.frame((subset(SP_Y_Returns,Sector=="Information Technology" | Sector=="Technology")))
techPerYear=as.data.frame(table(Tech_comps$year))
techPerYear$total=SP_Companies_per_year$total_winning
techPerYear$techPerc=techPerYear$Freq/techPerYear$total
techPerYear=rename(techPerYear,year=`Var1`, tech=`Freq`)

Tech_win=as.data.frame(table(subset(Tech_comps,yearly_return>mean(yearly_return))$year))
Tech_win=rename(Tech_win,year = `Var1`, winning = `Freq`)

# Number of companies with yearly return>0 per year
SP_Losing_comps=as.data.frame(table(subset(Tech_comps,yearly_return<mean(yearly_return))$year))
SP_Losing_comps=rename(SP_Losing_comps,year = `Var1`, losing = `Freq`)

# Merging above tables and summarizing it to create data for AD calculations 
AD_line_data=merge(Tech_win,SP_Losing_comps,by.x=1, by.y =1)
#AD_line_data$total=SP_Companies_per_year$total_winning
#AD_line_data$percWin=AD_line_data$winning/AD_line_data$total
#AD_line_data$percLose=AD_line_data$losing/AD_line_data$total
AD_line_data$WinLoseDiff=AD_line_data$winning-AD_line_data$losing

# Calculating AD_line 
AD_line_data$AD_line[1]=AD_line_data$WinLoseDiff[1]
for(i in 2:nrow(AD_line_data)){
  AD_line_data$AD_line[i]=AD_line_data$WinLoseDiff[i]+AD_line_data$AD_line[i-1]
}
plot(AD_line_data$year,AD_line_data$AD_line,main="Tech Industry Advance/Decline Line",xlab="Years",Ylab="AD_line(#win-#lost+AD(t-1) *t=Time",type="l",col="red")
lines(AD_line_data$year,AD_line_data$AD_line,type="l",col="red")

plot(AD_line_data$year,AD_line_data$WinLoseDiff,main="difference between winning and losing tech companies ",xlab="Years",Ylab="win-lose")
lines(AD_line_data$year,AD_line_data$WinLoseDiff,type="l",col="red")

plot(AD_line_data$year,Market_Return$market_return,type="l",col="green")
lines(AD_line_data$year,SP_Y_Returns$market_return,type="l",col="green")
write.csv(AD_line_data,file="Tech_AD_Line_data.csv")
```

Companies beating the market return  
```{r}
SP_Companies_per_year=as.data.frame(table(SP_Y_Returns$year))
SP_Companies_per_year=rename(SP_Companies_per_year,year = `Var1`, companies = `Freq`)

beat_the_market=as.data.frame(table(subset(SP_Y_Returns,yearly_return>market_return)$year))
beat_the_market=rename(beat_the_market, year = `Var1`, winning_companies = `Freq`)

less_than_market=as.data.frame(table(subset(SP_Y_Returns,yearly_return<market_return)$year))
less_than_market=rename(less_than_market,year = `Var1`, losing_companies = `Freq`)

line_data=merge(beat_the_market,less_than_market,by.x=1, by.y =1)
line_data$total=SP_Companies_per_year$companies
line_data$percWin=line_data$winning_companies/line_data$total
line_data$percLose=line_data$losing_companies/line_data$total
line_data$WinLoseDiff=line_data$winning_companies-line_data$losing_companies
```
